---
title: "École d'été 2023 - Introduction"
author: 
  - "Lars Vilhuber"
  - "Chishio Furukawa"
date: "`r Sys.Date()`"
output: 
  ioslides_presentation:
  incremental: false
self-included: true
widescreen: true
---
  
```{r, child=c('toc.md')}
```

## Details {.smaller}

- Welcome
- Overview
- Technical
- Imperfect example
  - [github.com/labordynamicsinstitute/very-imperfect-example](https://github.com/labordynamicsinstitute/very-imperfect-example)
  - How to download from Github: two ways
  - Let's replicate!

## Details {.smaller}

- Discussion 
- [how to install Stata packages](02-how-to-install-Stata-packages.html) 
  - More generally: the role of environments
- [Data provenance](07-data-provenance.html)       
  - What is it
  - Helping others find data

## Details {.smaller}

After lunch, more details.

## Détails {.smaller}

- 13:30 Side-note: how to run things in the cloud (90 minutes)
  - C'est quoi, le cloud?
  - Resources:
    - Python in the cloud ([Github Codespaces](https://github.com/codespaces), Google Colab, ...) 
    - Stata in the cloud! ([Github Codespaces with Stata](https://github.com/labordynamicsinstitute/codespaces-stata-skeleton), [CodeOcean](https://codeocean.com), [Wholetale](https://wholetale.org)) 
  - Try it out (need Github Account or CodeOcean Account or WholeTale account)
- 15:00 Break


## Détails {.smaller}

- 15:15 How to structure a project 
- 16:00 Try it out / Fin


# Day 2


```{r, child=c('toc2.md')}
```

## Détails {.smaller}

- 9:00 Documenting it all: the template README 
  - [https://social-science-data-editors.github.io/template_README/](https://social-science-data-editors.github.io/template_README/)

- 10:00 Data provenance
  - Data citations (15 min)
  - Data provenance: beyond citations
    - Complex examples: IPUMS, WDI, DHS
  - Source of the US Census data 
  - Authoritative vs. random sources

## Détails {.smaller}

- 10:30 When data cleaning is critical
  - Your project doesn't start with the analysis data (no "trust me")
  - Find the problem!
  - Try it out: 30 minutes

## Détails {.smaller}

- 11:00 Completing the template README
  - Documenting data provenance
  - The role of licenses and permissions 
- 12:00 Break (1h)

## Détails {.smaller}

- 13:00 Creating a replication package
  - So you have it all?
  - Let's try that again: Run your neighbor's replication package in 10 minutes
  - (30 minutes)
  
## Détails {.smaller}

- 13:30 Depositing a replication package
  - Gentle introduction to Zenodo (sandbox) (or Dataverse)
  - Uploading - Zipfiles vs. individual files?
  - Metadata
  - Pressing publish - what happens?
  - Updating a replication package
- 14:30  Break

## Détails {.smaller}

- 14:45 Wrap-up
  - Group discussion
  - Questions
- 16:00 (ou plus tôt): Fin.


```{r, child=c('toc.md')}
```

